### 2015-02-12 fundamentals/fcsreqs.tex
this attemps to provide a stronger literature review of existing simulators. It was based heavily on the functions and requirements, for obvious reasons... that document drove our devlopment.

@@

Similarly, the ability to model disruptions (i.e. facility shutdowns due to insufficient feed material or insufficient processing and storage capacity) is most readily captured by software capable of tracking the operations status of discrete facilities \cite{huff_functions_2010}.
Fleet-based models (i.e. \gls{VISION}) are unable to capture this gracefully. All of the software capable of discrete materials have a notion of discrete facilities, however not all handle disruption in the same manner. \gls{DESAE}, for example, does not allow shutdown due to insufficient feedstock, though \Cyclus does. In the event of insufficient fissile material during reprocessing, \gls{DESAE} borrows material from storage, leaving a negative value \macarthy_benchmark_2012}.

The proprietary concerns of research institutions and security constraints of data within fuel cycle codes often restrict code access. A code's use is therefore often limited to its institution of origin, necessitating effort duplication at other institutions and thereby squandering broader human resources. License agreements and institutional approval are required for most current codes (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, \gls{EVOLCODE}, \gls{FAMILY}, and \gls{NFCSIM})\cite{juchau_modeling_2010}. However, \Cyclus and the MIT code, \gls{CAFCA}, provides fully free and open access to all users and developers, foreign and domestic.

Uncertainty and Sensitivity Automation
While uncertainty and sensitivity analysis of input parameters can be conducted at a medium-fidelity level by manual parametric sampling with almost any fuel cycle code [26] [33], automated sampling and propagation of uncertainties and parametric sensitivity has not been achieved by any of the fuel cycle codes discussed here. Furthermore, uncertainty distributions for included data and propagation algorithms are lacking. Many of the missions that the FCS seeks to support would be facilitated by such a capability and this need constitutes a driving factor in the development of the FCS concept.

Unconventional Reactor Modeling
Much fuel cycle simulation focus in the recent decade has been driven by specific fuel cycle policy goals. As a result, most fuel cycle models have neglected to model myriad unconventional fuel cycles and reactor models on the research stage today. \Cyclus seeks to offer unconstrained modeling freedom for researchers interested in the impact of unconventional transmutation technologies and uses of reactor heat production on fuel cycle metrics. Such unconventional models may include advanced designs such as small modular reactors and travelling wave reactors.

Dynamic Feedback for Economic Analysis
In addition to recording cost information about deployment and material movements, \Cyclus simulation logic relies on a market paradigm that enables simulation of the dynamic responses within the system to pricing, availability, and other institutional preferences. This capability is an advanced functionality and does not exist in a flexible manner for other fuel cycle simulators.

>>>>

\subsubsection{Discrete Facilities and Materials}

@@

Similarly, the ability to model disruptions (i.e. facility shutdowns due to
insufficient feed material or insufficient processing and storage capacity) is
most readily captured by software capable of tracking the operations status of
discrete facilities \cite{huff_functions_2010}.  Fleet-based models (i.e.
\gls{VISION}) are unable to capture this gracefully.  All of the software
capable of discrete materials have a notion of discrete facilities, however not
all handle disruption in the same manner. \gls{DESAE}, for example, does not
allow shutdown due to insufficient feedstock, though \Cyclus does. In the event
of insufficient fissile material during reprocessing, \gls{DESAE} borrows
material from storage, leaving a negative value \cite{macarthy_benchmark_2012}.

\subsubsection{Open Access}

The proprietary concerns of research institutions and security constraints of
data within fuel cycle codes often restrict code access. A code's use is
therefore often limited to its institution of origin, necessitating effort
duplication at other institutions and thereby squandering broader human
resources. License agreements and institutional approval are required for most
current codes (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, \gls{EVOLCODE},
\gls{FAMILY}, and \gls{NFCSIM})\cite{juchau_modeling_2010}.  Even when, as in
the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
platform on which it relies is oftenrestricted or commercial.  However, \Cyclus
provide fully free and open access to all users
and developers, foreign and domestic.

\subsubsection{Flexibility and Extensibility}

In addition to being inaccessible, the vast majority of fuel cycle simulators
are, effectively, inextensible. Typical fuel cycle simulator evelopment teams are insular, in
part due to accessiblity issues. Also, however, their frameworks contain
heuristics and assumptions that constrain developer additions.

For example, where most other simulators describe a finite set of acceptable
cycle constructions (once through, single-pass, multi-pass), the \Cyclus
simulation logic relies on a market paradigm that can be easily directed to
create novel material and economic paths. The simulation of the dynamic
responses within the system to pricing, availability, and other institutional
preferences in \Cyclus is an advanced capability and does not exist in a
flexible manner for other fuel cycle simulators.

### 2015-02-12 fundamentals/intro.tex
this attemps to provide a stronger literature review of existing simulators. It was based heavily on the functions and requirements, for obvious reasons... that document drove our devlopment.

Historically, domestic national laboratories have driven development and regulated
the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010},
\gls{DANESS}\cite{van_den_durpel_daness_2009},
\gls{DYMOND}\cite{yacout_modeling_2005}, and
\gls{NFCSim}\cite{schneider_nfcsim:_2005}.
Internationally, other laboratories have created their own as well, such as
\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}
and
\gls{ORION}\cite{worrall_scenario_2007}.
Outside the national laboratories,
researchers have created new nuclear fuel cycle simulation tools when existing
tools were not available or not sufficiently general to calculate their metrics
of interest.  With limited access to the national
laboratory tools and a need to customize them for research purposes,
universities and private industry researchers have ``reinvented the wheel'' by
developing tools of their own from scratch and tailored to their own needs, for
example \gls{CAFCA}\cite{guerin_impact_2009}.

>>>>

Historically, domestic national laboratories have driven development and regulated
the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010},
\gls{DANESS}\cite{van_den_durpel_daness_2009},
\gls{DYMOND}\cite{yacout_modeling_2005}, and
\gls{NFCSim}\cite{schneider_nfcsim:_2005}.
Internationally, other laboratories have created their own as well, such as
\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}
and
\gls{ORION}\cite{worrall_scenario_2007}.
Outside the national laboratories,
researchers have created new nuclear fuel cycle simulation tools when existing
tools were not available or not sufficiently general to calculate their metrics
of interest.  With limited access to the national
laboratory tools and a need to customize them for research purposes,
universities and private industry researchers have ``reinvented the wheel'' by
developing tools of their own from scratch and tailored to their own needs.
